02_DESeq_characterization

### 2019-07-24 analysis/03_DESeq2_characterization.Rmd
musicgenes4

>>>>

musicgenes2 <- function(mygroup, mysusbtitle){

myplot <- candidataCountsTcol2 %>%
  filter(sextissue %in% c(mygroup)) %>%
ggplot(aes(x = treatment, y = mean)) +
  geom_point(colour = "white") + 
  theme_bw() +
  facet_wrap(~gene, scales = "free", ncol = 1) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_image(aes(image="https://storage.needpix.com/rsynced_images/music-34177_1280.png")) +
  labs(y = "mean gene expression", subtitle = mysusbtitle, x = NULL) +

a <- musicgenes2("female_hypothalamus", "female hypothalamus")
b <- musicgenes2("male_hypothalamus", "male hypothalamus")

pdf("../figures/characterization/musicalgenes-2.pdf", width = 8, height = 6)
plot(c)
dev.off()
